Using functor categories to generate intermediate code with Agda

### 2025-05-12 fig/implementation/dependencies.tex
Evaluation almost done
Evaluation and conclusion almost completed

		% Nodes
		\node (lib) {lib.agda};
		\node[below left=of lib] (source) {source.agda};
		\node[below right=of lib] (target) {target.agda};
		\node[below left=of target] (compiler) {compiler.agda};

		% Arrows
		\draw[arrow] (lib) -- (source);
		\draw[arrow] (lib) -- (target);
		\draw[arrow] (source) -- (compiler);
		\draw[arrow] (target) -- (compiler);
		\draw[arrow] (lib) -- (compiler);

>>>>

		% Nodes
		\node (lib) {\texttt{lib.agda}};
		\node[below left=of lib] (source) {\texttt{source.agda}};
		\node[below right=of lib] (target) {\texttt{target.agda}};
		\node[below =of lib] (compiler) {\texttt{compiler.agda}};
		\node[below =of compiler] (test) {\texttt{test.agda}};

		% Arrows
		\draw[arrow] (source) -- (lib);
		\draw[arrow] (target) -- (lib);
		\draw[arrow] (compiler) -- (source);
		\draw[arrow] (compiler) -- (target);
		\draw[arrow] (compiler) -- (lib);
		\draw[arrow] (test) -- (source);
		\draw[arrow] (test) -- (target);
		\draw[arrow] (test) -- (compiler);
